PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-24 paper/sec-pineappl.tex
Remind the reader where the indices are defined
Clarify that we use the same algorithm
Rewrite introduction of section 2

In this section we introduce \textsc{PineAPPL}. We first describe the
general scope and features of the library, we then formulate the problem of
computing Monte Carlo weights for cross sections in a multi-coupling expansion,
and we finally address how this problem is solved with a suitable grid
representation.

@@

A straightforward representation is provided by  4-tuples, a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
For each combination $(a,b,k,l,m,n,o)$ we save the following 4-tuples,
\begin{equation}
\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{.} \label{eq:four-tuples}
\end{equation}
The reconstruction of the differential cross section is then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.

@@

We use the same \enquote{Lagrange-interpolation grid} presented in ref.~\cite{Carli:2010rw} with the parameters published in ref.~\cite{Bertone:2014zva}, which give sufficient precision (see section~\ref{sec:results}).

>>>>

In this section we introduce \textsc{PineAPPL}.
We first describe the general scope and features of the library in comparison to \textsc{APPLgrid} and \textsc{fastNLO}.
Section~\ref{sec:multi-coupling-expansion} gives the details and, in particular, describes the problem of computing Monte Carlo weights for cross sections in a multi-coupling expansion; this section may be read first by readers unfamiliar with the programs mentioned previously.

@@

A straightforward representation is provided by  4-tuples, a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
For each combination $(a,b,k,l,m,n,o)$ (see section~\ref{sec:multi-coupling-expansion} for their definition) we save the following 4-tuples,
\begin{equation}
\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{.} \label{eq:four-tuples}
\end{equation}
The reconstruction of the differential cross section is then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.

@@

We use the same \enquote{Lagrange-interpolation grid} presented in ref.~\cite{Carli:2010rw} with the parameters published in ref.~\cite{Bertone:2014zva}, which give sufficient precision (see section~\ref{sec:results}).
For the sake of completeness, the following summarises the interpolation algorithm.
